Assessing rigor and impact of research software for hiring and promotion in psychology: A comment on Gärtner et al.~(2022)

### 2023-10-04 manuscript.Rmd
move correspondance

author: 
  - name          : "Andreas M. Brandmaier"
    affiliation   : "1,2,3"
    corresponding : yes    # Define only one corresponding author
    address       : "Rüdesheimer Str. 50, 14197 Berlin"
    email         : "andreas.brandmaier@medicalschool-berlin.de"
  - name          : "Maximilian Ernst"
    affiliation   : "2,4"
  - name          : "Aaron Peikert"
    affiliation   : "2,3,4"

@@

Put the contact information and any acknowledgements here. ORCID to all author if available. Corresponding author mandatory.
These headings after the article but before the references are required. Feel free to add other headings (e.g., acknowledgments) if you need to.

>>>>

author: 
  - name          : "Andreas M. Brandmaier"
    affiliation   : "1,2,3"
    corresponding : no    # Define only one corresponding author
    address       : "Rüdesheimer Str. 50, 14197 Berlin"
    email         : "andreas.brandmaier@medicalschool-berlin.de"
  - name          : "Maximilian Ernst"
    affiliation   : "2,4"
  - name          : "Aaron Peikert"
    affiliation   : "2,3,4"

@@

Correspondence concerning this article should be addressed to Andreas M. Brandmaier, Rüdesheimer Str. 50, 14197 Berlin.
E-mail: \href{mailto:andreas.brandmaier@medicalschool-berlin.de}{\nolinkurl{andreas.brandmaier@medicalschool-berlin.de}}
